---
title: "fasterr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Welcome to fasterr! This package is designed to optimize existing functions in the tidyr and stats packages. Let's get started by installing the package.

## Installation

First install the package by running:

```{r setup, eval=FALSE}
remotes::install_github("sds270-f24/fasterr")
```

Then, to load the package run this command:

```{r}
library(fasterr)
```

## Using the functions

To use fasterr's functions, simply call them like you would call the tidyr functions, but with fasterr::: before the function name. Here's some examples of how and when you might like to use each function:

### full_seq

If I had an incomplete sequence and I wanted to fill in the values with a certain interval between each element, I could use `full_seq`. Given an incomplete sequence and a step size, `full_seq` will return the sequence filled from the lowest to highest value with the specified step size between elements. Using `fasterr:::full_seq` will fill the sequence faster than the `tidyr` equivalent.

```{r eval=FALSE}
fasterr:::full_seq(c(1, 2, 5, 7), 1)
```

### fill_forward

If I had a `data.frame` with `NA` values, and I didn't want to omit them or keep them as `NA`, I could use fill_forward to fill each `NA` value with the last valid non `NA` value in the `data.frame`. This function takes in a `data.frame` and the columns in which you'd like the `NA` values to be filled. It will return the `data.frame` with all `NA` values from specified columns filled. Using `fasterr:::fill_forward` will fill the `data.frame` faster than the `tidyr` equivalent.

```{r eval=FALSE}
fasterr:::fill_forward(airquality,c("Ozone", "Solar.R"))
```

### omit_na
If I had a `data.frame` with `NA` values, I could use omit_na to remove the rows with `NA` values. This function takes in a `data.frame` as input and outputs the `data.frame` without the rows containing `NA`. The function stores information about which rows have been removed in an attribute of the cleaned `data.frame`.Using `fasterr:::omit_na` will remove `NA` values faster than the `tidyr` equivalent.
```{r eval=FALSE}
fasterr:::omit_na(airquality)
```
